---
writer: cwl
output:
  html_document:
    keep_md: yes
  pdf_document:
    latex_engine: xelatex
classoption: landscape
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

## Peer-graded Assignment 1: R Markdown and Leaflet
```{r echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
# Specify compilation date and time
format(Sys.time(), "%a %b %d %X %Y")
```

**Objective**
Create a web page using R Markdown that features a map created with Leaflet. 



We obtained a dataset about all Hospitals in Australia from [SpringerNature](https://springernature.figshare.com/articles/dataset/Hospital_IDs_names_and_coordinates_csv_/8319737/1), and aimed at display them on an interactive map, which was created by library(Leaflet).


This dataset consisted of names of hospitals in Australia, their geographic coordinates (Longitude and Latitude).

### 1. Load the data, library and perform some basic exploratory data analyses. 
```{r echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
library(dplyr); library(leaflet)
# Load data 
url <-"https://springernature.figshare.com/ndownloader/files/15591434"
hospital_df = read.csv(url, na.strings=c("NA","#DIV/0!",""))

# Inspect data
str(hospital_df)

# Select only necessary variables
hospital_df <- hospital_df %>%
    select(Latitude, Longitude, Hospital.name, Phone.number, Street.address, Postcode) %>%
    rename(lat=Latitude, lng=Longitude)

```

### 2. Create Hospital Map
```{r echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=9, fig.width = 9}
# Import hospital icon
hospitalIcon <- makeIcon(
  iconUrl = "./hospital.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)


# Function to create contents for popup
content <- function(name, phone, adr, code) {
    paste(sep = "<br/>",
          "<b>", name,"</b>",
          phone,
          adr, code)
}


# Create the Map
set.seed(Sys.Date())
hospital_df %>% 
    leaflet() %>%
    addTiles() %>%
    addMarkers(popup=content(hospital_df$Hospital.name,
                             hospital_df$Phone.number,
                             hospital_df$Street.address,
                             hospital_df$Postcode),
               clusterOptions = markerClusterOptions())
```
