---
title: "Quiz 3"
author: "cwl"
date: "6/1/2021"
output: html_document
---
### 1. 
Load the cell segmentation data from the AppliedPredictiveModeling package using the commands:
```{r echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
library(AppliedPredictiveModeling)
data(segmentationOriginal)
library(caret)
```

1. Subset the data to a training set and testing set based on the Case variable in the data set. 

2. Set the seed to 125 and fit a CART model with the rpart method using all predictor variables and default caret settings. 

3. In the final model what would be the final model prediction for cases with the following variable values:

a. TotalIntench2 = 23,000; FiberWidthCh1 = 10; PerimStatusCh1=2 
b. TotalIntench2 = 50,000; FiberWidthCh1 = 10;VarIntenCh4 = 100 
c. TotalIntench2 = 57,000; FiberWidthCh1 = 8;VarIntenCh4 = 100 
d. FiberWidthCh1 = 8;VarIntenCh4 = 100; PerimStatusCh1=2 



```{r echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
inTrain <- createDataPartition(y = segmentationOriginal$Case, p = 0.6, list = FALSE)
training <- segmentationOriginal[inTrain,] # split dataset
testing <- segmentationOriginal[-inTrain,]

set.seed(125)
modFit <- train(Class ~ .,method="rpart",data=training)

library(rattle)
fancyRpartPlot(modFit$finalModel)
```

### 2
Load the olive oil data using the commands:
```{r echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
library(pgmm)
data(olive)
olive = olive[,-1]
```
These data contain information on 572 different Italian olive oils from multiple regions in Italy. Fit a classification tree where Area is the outcome variable. Then predict the value of area for the following data frame using the tree command with all defaults

newdata = as.data.frame(t(colMeans(olive)))

What is the resulting prediction? Is the resulting prediction strange? Why or why not?
```{r echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
library(caret)
library(pgmm)
data(olive)
olive = olive[,-1]

head(olive)

modFit <- train(Area ~ .,method="rpart",data=olive)

library(rattle)
fancyRpartPlot(modFit$finalModel)

newdata = as.data.frame(t(colMeans(olive)))
predict(modFit, newdata = newdata)

```


