---
title: "Text Suggestion Presentation"
subtitle: "https://cwl286.shinyapps.io/TextSuggestion/"
author: "cwl"
output:
  ioslides_presentation:
    css: ./data/presentation/style.css
    smaller: yes
    transition: faster
---


## Introduction
<h3>Objective</h3>
- Build a predictive model of English text
- Develop an interface for our model via a Shiny application.
- When a user type text, he can see predictions for his next word


<h3>Background</h3>
- Final task in the [Data Science Capstone](https://www.coursera.org/learn/data-science-project?specialization=jhu-data-science) to create a usable data product 

<h3>Data</h3>
- Provided by the [Data Science Capstone](https://www.coursera.org/learn/data-science-project?specialization=jhu-data-science)
- en_US.blogs.txt, en_US.news.txt, en_US.twitter.txt


## Model
- Apply [N-gram](https://en.wikipedia.org/wiki/N-gram) to build our model
- (N-gram: a contiguous sequence of n items from a given sample of text)

<h3>Preprocessing</h3>
- Remove URLs
- Remove punctuation
- Remove numbers
- Remove English stopwords
- Remove special characters

<h3>N-gram</h3>
- Train Bigram, Trigram, 5-grams and 7-gram

## Application Features
- Automatic suggestion
- Build your own model
- Generate "composition"
- Interactive selection
- Suggestion visualization

<h3> How to use</h3>

- Type a text for suggestions for the next word. Suggested words are in the Wordcloud and the bar chart.
- Click the word cloud and the bar chart as an input
- Suggestions are automatically updated if Auto-Suggestion is selected
- Can build your model by uploading a text file. 
- After you built your model, you can select to use our default model or your prediction model.
- Our application can generate an English-like composition based on your input.


## Futher Information
- Shiny application: [Text Suggestion](https://cwl286.shinyapps.io/TextSuggestion/)
- View [Source](https://github.com/cwl286/datasciencecoursera/tree/master/10DataScienceCapstone/TextSuggestion)
- View course information [(Data Science Capstone)](https://www.coursera.org/learn/data-science-project?specialization=jhu-data-science)
- Report [bug](https://github.com/cwl286/datasciencecoursera/issues)

```{r fig.width=5, fig.height=3,echo=FALSE}
library(png)
library(grid)
img <- readPNG("./data/presentation/click.png")
 grid.raster(img)
```
```{r fig.width=2.5, fig.height=4,echo=FALSE}
img2 <- readPNG("./data/presentation/user.png")
 grid.raster(img2)
```



