---
title: "R Markdown Presentation & Plotly"
author: "cwl"
date: "6/4/2021"
output: ioslides_presentation
---


## Objective

The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?


## 1. Load the mtcars data
We use mtcars data for this presentation. This is the data structure:

1.	MPG	Miles/(US) gallon
2.	cyl	Number of cylinders
3.	disp	Displacement (cu.in.)
4.	hp	Gross horsepower
5.	drat	Rear axle ratio
6.	wt	Weight (1000 lbs)
7.	qsec	1/4 mile time
8.	vs	Engine (0 = V-shaped, 1 = straight)
9.	am	Transmission (0 = automatic, 1 = manual)
10.	gear	Number of forward gears
11.	carb	Number of carburetors


## 1. Load the mtcars data (cont.)

```{r echo = TRUE, comment = "", message=FALSE, cache=TRUE}
# Load library
require("plotly")
# Load data
data(mtcars)
# Specify compilation date and time
format(Sys.time(), "%a %b %d %X %Y")
```
---

```{r echo = TRUE, comment = "", message=FALSE, cache=TRUE, warning=FALSE, }
# data summary
summary(mtcars)
```

## 2. Plot 3D scatterplot
```{r echo = FALSE, comment = "", message=FALSE, warning=FALSE, cache=TRUE, fig.height=5, fig.width = 5}
color_palette <-  colorRampPalette(c("red","blue"))

plot_ly() %>%
    add_trace(df = ~mtcars, x =  mtcars$wt, y = mtcars$qsec, z = mtcars$mpg, 
              type = "scatter3d", mode = "text+markers", 
              color = factor(mtcars$am), colors = color_palette(2),
              marker = list(size = 6)) %>%
    layout(scene = list(xaxis = list(title = 'Weight'),
                    yaxis = list(title = '1/4 mile time'),
                    zaxis = list(title = 'mpg'))) 
```

